`r glue::glue('Doublet benchmarking results: {params$dataset}')`

### 2024-05-30 analyses/doublet-detection/template-notebooks/02_explore-benchmark-results.Rmd
add missing jitter plot
ground truth context

The goal of this notebook is to explore doublet inferences run on ground-truth benchmarking data. 
These three doublet detection methods are explored.

@@

>>>>

The goal of this notebook is to explore doublet inferences run on ground-truth benchmarking data. 
Importantly, the ground-truth doublets in these benchmarking datasets were themselves called with computational approaches in the context of multiplexed experiments.
This means the true values are not necessarily entirely accurate.

These three doublet detection methods are explored:

@@

```{r}
plot_jitter_scores(
  doublet_df,
  scrublet_score,
  scrublet_prediction,
  "scrublet prediction"
)
```
